How does the frequency and duration of social media usage correlate with indicators of mental health, such as anxiety and depression, among adolescents aged 13-19?

### 2024-04-17 output/paper/paper.qmd
making the structure better

# Import the dataset from a CSV file
df <- read.csv("C:/Users/ragha/Desktop/How does the frequency and duration of social media usage correlate with indicators of mental health, such as anxiety and depression, among adolescents aged 13-18/data/social_media_mental_health.csv")
# Change the file location to wherever your file is located.

>>>>

# Import the dataset from a CSV file
df <- read.csv("C:/Users/ragha/Desktop/How does the frequency and duration of social media usage correlate with indicators of mental health, such as anxiety and depression, among adolescents aged 13-18/input/data/social_media_mental_health.csv")
# Change the file location to wherever your file is located.
